### 2019-05-30 treestats_paper.tex
tweak to L

Suppose we have genotyped a collection of $N$ (homologous) chromosomes
at a sequence of $G$ loci along the genome,
and wish to compute statistic of the allele frequency spectrum.
In other words, if the frequency of allele $a$ at a site $i$ is $p_i(a)$,
and the allele frequency spectrum
-- i.e., the proportion of alleles whose frequency is $p$ in our sample -- is $f(p)$,
then for some function $h()$ we want to compute $\sum_p f(p) h(p)$.
Since this is a simple average over sites,
we can compute this, summing over the $L$ sites, as
$$\sum_p f(p) h(p) = (1/G) \sum_{i=1}^G \sum_a h(p_i(a)).$$
(Note that since the ancestral allele is included, this is a function of the 
\emph{folded} frequency spectrum, so is invariant to relabeling of alleles.)
If we know where each mutation has occurred on the genealogy,
we can easily find the frequency of the corresponding allele by counting how many samples
occur below that mutation in the tree (and accounting for those that subsequently mutate).
What we do here is a generalization of this idea.

>>>>

Suppose we have sequenced a linear genome of $L$ bases from $n$ (homologous) sampled chromosomes,
and wish to compute a statistic of the allele frequency spectrum.
In other words, if the frequency of allele $a$ at a site $i$ is $p_i(a)$,
and the allele frequency spectrum
-- i.e., the proportion of alleles whose frequency is $p$ in our sample -- is $h(p)$,
then for some function $f()$, we want to compute $\sum_p h(p) f(p)$.
Since this is a simple average over sites, and monomorphic sites do not contribute,
we can compute this, summing over the $L$ loci, as
$$\sum_p h(p) f(p) = (1/L) \sum_{i=1}^L \sum_a f(p_i(a)).$$
(Note that since the ancestral allele is included, this is a function of the 
\emph{folded} frequency spectrum, so is invariant to relabeling of alleles.)
If we know where each mutation has occurred on the genealogy,
we can easily find the frequency of the corresponding allele by counting how many samples
occur below that mutation in the tree (and accounting for those that subsequently mutate).
What we do here is a generalization of this idea.
